\section{Conclusion}
\label{sec:acc-conclusion}

Further things to do:
\begin{enumerate}
  \item Rethink the multithreading part (need some help here)

  \item Explain how and why I eliminated the first hotspot (that I considered
  redundant). Should I email the guys that made the graph and ask them about it?
  I seriously doubt they remember anymore.

  \item \sout{Include profiling data after eliminating the hotspot above and} draw some
  conclusions

  \item \sout{Profile on ARM (and hope the results coincide with the ones
  above)}

  \item \label{li-test1} \sout{Test the kernel on ARM + Connex} Find what's
  wrong with the results on Connex.

  \item Integrate the kernel in the graph, test it, profile it and compare

  \item For testing in \ref{li-test1}: \sout{Create some files with random data
  generated in Octave along with the expected results and maybe} integrate with
  gtest? 

  \item Autocorrelation
    \begin{enumerate}
      \item Make kernel more efficient (think about how to process/prepare data
      so as to not wait too much). 
      \item How expensive is the writeDataToArray? Is it okay to load everything
      in one chunk?
      \item How to do the index loading more efficiently? If it isn't possible
      to give the line and column indices as arguments to a function, maybe
      create a big array with possible indices and just send some parts to the
      kernel? This instead of the current version, which at each iteration
      deletes the current items and allocates memory for the new index.
      \item Do the backward averaging part on the kernel too?
      \item Integrate into gr-doa
    \end{enumerate}

  \item Decide what parts from the past reports will be in the final thesis and
  assemble them. I think I'll have enough pages, so that shouldn't be the
  problem, but instead choose what's important to include.

  \item Less important but still: ask someone about the style of the code in the
  thesis. The official template that I have draws ugly boxes around references
  and I'm not sure it's ok. Also, I don't know about the style of the code
  included.

\end{enumerate}
